Resurgence of the Airy function \\ and other exponential integrals

### 2022-08-19 exp-resurgence.tex
Rescale `z` for nicer series
Sketch ODE example

\begin{document}
\maketitle
\section{Introduction}
\subsection{Motivation}
\subsubsection{Setting}
You can often find a formal power series
\[ \series{\Phi} = z^\sigma \left( \frac{c_0}{z} + \frac{c_1}{z^2} + \frac{c_2}{z^3} + \frac{c_3}{z^4} + \ldots \right), \]
with $\sigma \in [0, 1)$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, you might rewrite the integral
\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du \]
as
% see expansion.sage
\[ e^z \int_{\Lambda} e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \left(\frac{\tau}{\sqrt{12}}\right) + \frac{5}{6} \left(\frac{\tau}{\sqrt{12}}\right)^2 - \frac{32}{27} \left(\frac{\tau}{\sqrt{12}}\right)^3 + \frac{385}{216} \left(\frac{\tau}{\sqrt{12}}\right)^4 + \ldots \right] \frac{d\tau}{\sqrt{12}} \]
using the substitution $\tfrac{1}{2} \tau^2 = 4u^3 - 3u + 1$.

>>>>

\begin{document}
\maketitle
\section{Introduction}
\subsection{Motivation}
\subsubsection{Setting}
You can often find a formal power series
\[ \series{\Phi} = z^\sigma \left( \frac{c_0}{z} + \frac{c_1}{z^2} + \frac{c_2}{z^3} + \frac{c_3}{z^4} + \ldots \right), \]
with $\sigma \in [0, 1)$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, you might rewrite the integral
\color{DodgerBlue}
\[ \Phi(z) = \int_{\Lambda} \exp\left[-\tfrac{1}{12} z \left(4u^3 - 3u\right)\right]\,du \]
\color{black}
\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(\tfrac{1}{3} u^3 - \tfrac{1}{4} u\right)\right]\,du \]
as
% see expansion.sage
\[ e^{z/12} \int_{-\infty}^\infty e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \tau + \frac{5}{6} \tau^2 - \frac{32}{27} \tau^3 + \frac{385}{216} \tau^4 - \frac{224}{81} \tau^5 + \frac{17017}{3888} \tau^6 - \ldots \right] d\tau \]
using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you get the series
\color{DodgerBlue}
\[ e^{z/12} z^{-1/2} \left[ (-1)!! + \frac{5}{6}\,1!!\,z^{-1} + \frac{385}{216}\,3!!\,z^{-2} + \ldots \right] \]
\[ e^{z/12} z^{1/2} \left[ \frac{(-1)!!}{z} + \frac{5}{6} \cdot \frac{1!!}{z^2} + \frac{385}{216} \cdot \frac{3!!}{z^3} + \frac{17017}{3888} \cdot \frac{5!!}{z^4} + \ldots \right] \]
\color{black}
\begin{equation}
e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
which has zero radius of convergence, but still makes sense as a formal power series. As another example, if you want to construct a holomorphic function $\Phi$ that satisfies the ordinary differential equation (ODE)
\begin{center}
\textbf{[shifted Bessel matching example above]},
\end{center}
you might start by trying to construct a formal power series solution instead. Observing that the leading term must be a multiple of $z^{-1/2}$ and then extending term by term, you again \textcolor{magenta}{[check]} get series~\eqref{series:bessel-ex}.
